Supplemental Material for: The evolution of gene expression in the term placenta of viviparous mammals

### 2016-01-29 manuscript/supplemental_material.Rnw
move more trees to supplemental

@@

>>>>

\begin{figure}
<<fstl1.evolution.tree,echo=FALSE,fig.width=12,fig.height=12,warning=FALSE,message=FALSE>>=

tree.id <-
    genes.to.tree[combined.fpkm[gene_short_name=="FSTL1" & species=="homo sapiens",gene_id],tree]
gene.tree.table <- trees[[tree.id]]$table
gene.tree.expression <- combined.fpkm[gene_id %in% gene.tree.table[,gene_id]]
gene.tree <- read.tree(text=trees[[tree.id]]$tree.dat)
plot.tree.matrix(read.tree(text=trees[[tree.id]]$tree.dat),gene.tree.table,gene.tree.expression,min.fpkm=5)
@ 
\caption{\genetreeexplanation{follistatin-like 1 \textit{FSTL1}}}
\label{fig:fstl1_evolution_tree}
\end{figure}

\begin{figure}
<<serpine.evolution.tree,echo=FALSE,fig.width=12,fig.height=12,warning=FALSE,message=FALSE>>=

tree.id <-
    genes.to.tree[combined.fpkm[gene_short_name=="SERPINE2" & species=="homo sapiens",gene_id],tree]
gene.tree.table <- trees[[tree.id]]$table
gene.tree.expression <- combined.fpkm[gene_id %in% gene.tree.table[,gene_id]]
gene.tree <- read.tree(text=trees[[tree.id]]$tree.dat)
plot.tree.matrix(read.tree(text=trees[[tree.id]]$tree.dat),gene.tree.table,gene.tree.expression,min.fpkm=1)
@ 
\caption{\genetreeexplanation{\textit{SERPINE2}}}
\label{fig:serpine_evolution_tree}
\end{figure}

\begin{figure}
<<estrogen.evolution.tree,echo=FALSE,fig.width=12,fig.height=12,warning=FALSE,message=FALSE>>=

tree.id <-
    genes.to.tree[combined.fpkm[gene_short_name=="CYP19A1" & species=="homo sapiens",gene_id],tree]
gene.tree.table <- trees[[tree.id]]$table
gene.tree.expression <- combined.fpkm[gene_id %in% gene.tree.table[,gene_id]]
gene.tree <- read.tree(text=trees[[tree.id]]$tree.dat)
plot.tree.matrix(read.tree(text=trees[[tree.id]]$tree.dat),gene.tree.table,gene.tree.expression)
@ 
\caption{\genetreeexplanation{estrogen synthesis genes}}
\label{fig:estrogen_evolution_tree}
\end{figure}

\begin{figure}
<<progesterone.evolution.tree,echo=FALSE,fig.width=12,fig.height=12,warning=FALSE,message=FALSE>>=

tree.id <-
    genes.to.tree[combined.fpkm[gene_short_name=="HSD3B1" & species=="homo sapiens",gene_id],tree]
gene.tree.table <- trees[[tree.id]]$table
gene.tree.expression <- combined.fpkm[gene_id %in% gene.tree.table[,gene_id]]
gene.tree <- read.tree(text=trees[[tree.id]]$tree.dat)
plot.tree.matrix(read.tree(text=trees[[tree.id]]$tree.dat),gene.tree.table,gene.tree.expression,
                 subtree=c("ENSMODG00000005385","ENSLAFG00000027896")
                 )
@ 
\caption{\genetreeexplanation{progesterone synthesis genes}}
\label{fig:progesterone_evolution_tree}
\end{figure}

\begin{figure}
<<chorionic.somatomammotropin.evolution.tree,echo=FALSE,fig.width=12,fig.height=12,warning=FALSE,message=FALSE>>=

tree.id <-
    genes.to.tree[combined.fpkm[gene_short_name=="CSH1" & species=="homo sapiens",gene_id],tree]
gene.tree.table <- trees[[tree.id]]$table
gene.tree.expression <- combined.fpkm[gene_id %in% gene.tree.table[,gene_id]]
gene.tree <- read.tree(text=trees[[tree.id]]$tree.dat)
plot.tree.matrix(read.tree(text=trees[[tree.id]]$tree.dat),gene.tree.table,gene.tree.expression)
@ 
\caption{\genetreeexplanation{chorionic somatomammotropin}}
\label{fig:csh1_evolution_tree}
\end{figure}

\begin{figure}
<<prolactin.evolution.tree,echo=FALSE,fig.width=12,fig.height=12,warning=FALSE,message=FALSE>>=

tree.id <-
    genes.to.tree[combined.fpkm[gene_short_name=="PRL" & species=="homo sapiens",gene_id],tree]
gene.tree.table <- trees[[tree.id]]$table
gene.tree.expression <- combined.fpkm[gene_id %in% gene.tree.table[,gene_id]]
gene.tree <- read.tree(text=trees[[tree.id]]$tree.dat)
plot.tree.matrix(read.tree(text=trees[[tree.id]]$tree.dat),gene.tree.table,gene.tree.expression)
@ 
\caption{\genetreeexplanation{prolactin}}
\label{fig:prolactin_evolution_tree}
\end{figure}

@@

\begin{table}
  \footnotesize
<<rodentia.lineage.specific,echo=FALSE,results="asis">>=
rod.all.lin.spec <- placenta.lineage.specific.table("rod.all")
setkey(rod.all.lin.spec,"Human Symbol")
@ 
\caption{Genes whose expression changed significantly in the Rodentia
  order as compared to all other analyzed species.}
\label{tab:rodentia_lineage_specific}
\end{table}
